---
title: "Predictive Modeling: Performance Report"
output: 
  flexdashboard::flex_dashboard:
    logo: logo.png
    css: styles.css
---

<script>
function bgExpand(x) {
    var text = window.getComputedStyle(x, ":before").getPropertyValue("content");
    if (text === '"+"') {
        x.setAttribute("data-text", "-");
        x.parentElement.parentElement.parentElement.parentElement.parentElement.getElementsByClassName("pc-section")[0].parentElement.style.display = "none";
        window.dispatchEvent(new Event('resize'));
    } else {
        x.setAttribute("data-text", "+");
        x.parentElement.parentElement.parentElement.parentElement.parentElement.getElementsByClassName("pc-section")[0].parentElement.style.display = "flex";
        window.dispatchEvent(new Event('resize'));
    }
}
function pcExpand(x) {
    var text = window.getComputedStyle(x, ":before").getPropertyValue("content");
    if (text === '"+"') {
        x.setAttribute("data-text", "-");
        x.parentElement.parentElement.parentElement.parentElement.parentElement.getElementsByClassName("bg-section")[0].parentElement.style.display = "none";
        window.dispatchEvent(new Event('resize'));
    } else {
        x.setAttribute("data-text", "+");
        x.parentElement.parentElement.parentElement.parentElement.parentElement.getElementsByClassName("bg-section")[0].parentElement.style.display = "flex";
        window.dispatchEvent(new Event('resize'));
    }
}
</script>

Gains Charts {data-icon="fa-table"}
===================================

<h2 class="project-label">%s</h2>

Column {.tabset}
------

### <span class="page-title"><span class="page-title-fa fa fa-table"></span>Build</span>

```{r}
x$build$gcDT
```

### <span class="page-title"><span class="page-title-fa fa fa-table"></span>Validate</span>

```{r}
x$validate$gcDT
```

Quantile Graphs {data-icon="fa-bar-chart"}
==========================================

<h2 class="project-label">%s</h2>

Column
------

### <span class="page-title"><span class="page-title-fa fa fa-bar-chart"></span>Mean Outcome<span class="expand-button" data-text="+" onclick="bgExpand(this)"></span></span>{.bg-section}

```{r}
x$both$gcBG
```

Column
------

### <span class="page-title"><span class="page-title-fa fa fa-line-chart"></span>Cumulative Performance<span class="expand-button" data-text="+" onclick="pcExpand(this)"></span></span>{.pc-section}

```{r}
x$both$gcPC
```
